---
title: "QTL0001 - Ineligibility"
---

# QTL0001 - Ineligibility

## Study Overview
```{r, echo=FALSE}
gsm.qtl::QTL_Overview(dfResults = qtl0001_params$dfResults,
             dSnapshot = qtl0001_params$latest_snapshot,
             strNum = "Ineligible Participants",
             strDenom = "Total Enrolled", 
             strQTL = "Current Ineligible Enrolled Rate")
```

## Time Series Chart
```{r, echo=FALSE, results='asis', fig.height=4}
gsm.qtl::QTL_lineplot_v2(dfResults = qtl0001_params$dfResults, strQTL = "Ineligibility Rate")
```

## Bar Charts {.tabset .tabset-pills}

<<<<<<< fix-90-namespace-report-functions
```{r, eval = FALSE , echo = FALSE, results = 'asis', fig.height=4}
### JS - Site
# gsm.qtl::Widget_BarChartQTL(
#   dfResults = dplyr::filter(dfResults, GroupLevel == "Site", SnapshotDate == latest_snapshot, GroupID != "Upper_funnel"),
#   dfGroups = dfGroups,
#   strOutcome = "Metric"
# )
```

### Site
```{r, echo = FALSE, results = 'asis', fig.height=4}
gsm.qtl::eligibility_groupBar(df = qtl0001_params$dfListing, varGroupID = invid, strGroupLabel = "Site")
=======
### Site
```{r, echo = FALSE, results = 'asis', fig.height=4}
eligibility_groupBar(dfNum = qtl0001_params$dfNum, dfDenom = qtl0001_params$dfDenom, varGroupID = invid, strGroupLabel = "Site")
>>>>>>> fix-90
```

### Country
```{r, echo = FALSE, results = 'asis', fig.height=4}
<<<<<<< fix-90-namespace-report-functions
gsm.qtl::eligibility_groupBar(df = qtl0001_params$dfListing, varGroupID = country, strGroupLabel = "Country")
=======
eligibility_groupBar(dfNum = qtl0001_params$dfNum, dfDenom = qtl0001_params$dfDenom, varGroupID = country, strGroupLabel = "Country")
>>>>>>> fix-90
```

### Source
```{r, echo = FALSE, results = 'asis', fig.height=4}
<<<<<<< fix-90-namespace-report-functions
gsm.qtl::eligibility_sourceBar(df = qtl0001_params$dfListing)
=======
eligibility_sourceBar(df = qtl0001_params$dfNum)
>>>>>>> fix-90
```

### Criteria/Site (EDC I/E data only)
```{r, echo = FALSE, results = 'asis', fig.height=4}
<<<<<<< fix-90-namespace-report-functions
gsm.qtl::criteria_groupBar(df = qtl0001_params$dfListing, varGroupID = invid, strGroupLabel = "Site")
=======
criteria_groupBar(df = qtl0001_params$dfNum, varGroupID = invid, strGroupLabel = "Site")
>>>>>>> fix-90
```

### Criteria/Country (EDC I/E data only)
```{r, echo = FALSE, results = 'asis', fig.height=4}
<<<<<<< fix-90-namespace-report-functions
gsm.qtl::criteria_groupBar(df = qtl0001_params$dfListing, varGroupID = country, strGroupLabel = "Country")
=======
criteria_groupBar(df = qtl0001_params$dfNum, varGroupID = country, strGroupLabel = "Country")
>>>>>>> fix-90
```

### Site/Criteria (EDC I/E data only)
```{r, echo = FALSE, results = 'asis', fig.height=4}
<<<<<<< fix-90-namespace-report-functions
gsm.qtl::criteria_groupBar(df = qtl0001_params$dfListing, varGroupID = invid, strGroupLabel = "Site", bSwapAxes = TRUE)
=======
criteria_groupBar(df = qtl0001_params$dfNum, varGroupID = invid, strGroupLabel = "Site", bSwapAxes = TRUE)
>>>>>>> fix-90
```

### Country/Criteria (EDC I/E data only)
```{r, echo = FALSE, results = 'asis', fig.height=4}
<<<<<<< fix-90-namespace-report-functions
gsm.qtl::criteria_groupBar(df = qtl0001_params$dfListing, varGroupID = country, strGroupLabel = "Country", bSwapAxes = TRUE)
=======
criteria_groupBar(df = qtl0001_params$dfNum, varGroupID = country, strGroupLabel = "Country", bSwapAxes = TRUE)
>>>>>>> fix-90
```

## Inclusion/Exclusion Listing
```{r, echo = FALSE}
# output the listing on the html
<<<<<<< fix-90-namespace-report-functions
gsm.qtl::eligibility_listing(df = qtl0001_params$dfListing)

# grab the dataset to download
x <- gsm.qtl::eligibility_listing(df = qtl0001_params$dfListing, download = TRUE)
csv_txt <- paste(utils::capture.output(utils::write.csv(x, row.names = FALSE)), collapse = "\n")# turn into a data-URI (single-file HTML friendly)
=======
eligibility_listing(df = qtl0001_params$dfNum)

# grab the dataset to download
x <- eligibility_listing(df = qtl0001_params$dfNum, download = TRUE)
csv_txt <- paste(capture.output(write.csv(x, row.names = FALSE)), collapse = "\n")# turn into a data-URI (single-file HTML friendly)
>>>>>>> fix-90
href <- base64enc::dataURI(charToRaw(csv_txt), mime = "text/csv;charset=utf-8")

knitr::asis_output(
  sprintf('<p><a class="btn btn-primary" download="eligibility_listing.csv" href="%s">
            ⬇️ Download CSV
          </a></p>', href)
)
```
